---
title: "Templating"
output: rmarkdown::html_vignette
description: |
    Templating is the a quick investigation of setting up templates.
vignette: >
  %\VignetteIndexEntry{Templating}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

Many different source of information were used to put together this template packages and its worth documenting them all for easy review.

* [R packages](https://r-pkgs.org/website.html) - covers general R package development
* [precommit](https://pre-commit.com/) - covers general precommit setups
* [r precommit](https://github.com/lorenzwalthert/precommit) - covers some extra r specific precommits
* [pkgdown](https://pkgdown.r-lib.org/) - for building general packages from R documentation

This template package used these resources to try and give an example that has:
1. Automatic production of code documention
2. Automatic pre-commit running of code checks and tests
3. Some Continuous Integration (CI) / Continuous Deployment (CD) pipelines in Github
4. An automatically built package website
5. Experiments with the R package building process
6. Suitable testthat R examples and linkages for CI / CD
7. Key vignettes showing relevant background information

```{r setup}
library(packTemplate)
```

