---
title: "Templating"
output: rmarkdown::html_vignette
description: |
    Templating is the a quick investigation of setting up templates.
vignette: >
  %\VignetteIndexEntry{Templating}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

Many different source of information were used to put together this template packages and its worth documenting them all for easy review.

* [R packages](https://r-pkgs.org/website.html) - covers general R package development
* [precommit](https://pre-commit.com/) - covers general precommit setups
* [r precommit](https://github.com/lorenzwalthert/precommit) - covers some extra r specific precommits
* [pkgdown](https://pkgdown.r-lib.org/) - for building general packages from R documentation
* [change-pkg-name](https://www.njtierney.com/post/2017/10/27/change-pkg-name/) - for thinking of how to change the package name

This template package used these resources to try and give an example that has:
1. Automatic production of code documention
2. Automatic pre-commit running of code checks and tests
3. Some Continuous Integration (CI) / Continuous Deployment (CD) pipelines in Github
4. An automatically built package website
5. Experiments with the R package building process
6. Suitable testthat R examples and linkages for CI / CD
7. Key vignettes showing relevant background information

```{r setup}
library(packTemplate)
packTemplate::hello()
packTemplate::df_shape_log_message(cars)
```

We also think to the set of [usethis](https://usethis.r-lib.org/reference/index.html) commands that were involved in setting up this template package for reference.

Please also note that these aren't all run at once and not all necessarily used in this specific package. i.e some may depend on setting up a github remote not defined in these checks

``` r
# initialising a package with version control and a license
usethis::create_package("path_to_package")'
# usethis::create_project()  # alternative that creates Rstudio rpoj files
usethis::use_git()
usethis::use_mit_license()

# Set it up to use testing + github
usethis::use_testhat()
usethis::use_readme_rmd()  # Adds a .rmd readme file which gets compiled to an readme.md
usethis::use_news_md()  # Adds a NEWS.md file for storing notes on version changes and releases
usethis::use_github_links()  # Add link of github remote to dscription file
usethis::use_roxygen_md()  # Use roxygen with markdown for documentation
# usethis::use_github()  # I didn't use this here but can set up a new git repository

# For adding packages in teh dependencies
usethis::use_package("glue")

# Optional for certain chages
# usethis::rename_files(old, new)  # Manages renaming tests, and source files to match new name
# usethis::use_r() to create new r file
# usethis::use_test() to create testing file for the R file

# Setting up many TidyVerse style defaults
usethis::use_tidy_issue_template()  # Adds the tidyverse issue template by default. It asks for a repex of the issue
usethis::use_tidy_contributing()  # Adds the tidy version contribution guidelines to the package
usethis::use_tidy_coc()  # Adds tidyverse code of conduct to the package

# Add relevant badges to the project - by default added to readme file
usethis::use_lifecycle_badge("experimental")
# use_cran_badge()  # Would use if release to CRAN to indicate the latest CRAN release

# Adding github actions for implementing parts of the CI / CD desires
# Lots of good github action examples here: https://github.com/r-lib/actions/tree/v2/examples
usethis::use_github_action("check-standard")  # Runs R CMD Check on a few operating systems
# usethis::use_github_action("test-coverage")  # Running test-coverage on push - USES EXTERNAL SERVICE, don't run unless code is public
usethis::use_github_action("pr-commands")  # To enforce document update + styler use in code on pull requests
usethis::use_pkgdown_github_pages()  # Sets up github
usethis::use_github_action("lint-project")  # Sets up linting to run on package commit and check for R syntax errors

# version increments
usethis::use_version(which = "patch")

# Setting up more examples for people to learn from

# Set some options in the R project to my preferred
usethis::use_blank_slate(scope = "project")  # Sets R project to not keep R workspace
```

The last very important part of this setup is establishing the git pre-commit hooks appropriately.
